---
title: "block_silhouette_cogsci2020"
author: "wmccarthy & jefan"
date: "1/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(broom)
library(tidyverse)
library(tidyboot)
library(knitr)
library(ggplot2)
library(ggthemes)
library(broom)
library(lme4)
library(lmerTest)
knitr::opts_chunk$set(echo = TRUE)
```

## Import data and apply preprocessing

```{r import}
df.full = read.csv('../results/csv/block_silhouette_Exp2Pilot3_good.csv')

d <- df.full %>% 
  select(rawF1DiscreteScore,phase,condition,trialNum,targetName,gameID,numBlocks,repetition,blockFell,buildTime,buggy) %>% 
  rename('accuracy'='rawF1DiscreteScore') %>%
  mutate(phase=relevel(phase, ref='pre')) %>%
  mutate(blockFell = as.logical(blockFell)) %>%
  mutate(repetition_1 = repetition + 1)

```

## Inspect data frame
```{r}
d
``` 

## Modeling effect of phase x condition on accuracy (F1 score)

Linear mixed effects models predicting rawF1DiscreteScore
```{r lmers}
## fit model to data just comparing pre/post
dpp <- d %>% filter(phase %in% c('pre','post')) 
m1 <- lmer(data = dpp, accuracy ~ phase + (1 | gameID) + (1 | targetName))
m2 <- lmer(data = dpp, accuracy ~ condition + (1 | gameID) + (1 | targetName))
m3 <- lmer(data = dpp, accuracy ~ phase + condition + (1 | gameID) + (1 | targetName))
m4 <- lmer(data = dpp, accuracy ~ phase * condition + (1 | gameID) + (1 | targetName))
anova(m1,m2,m3,m4)
summary(m4)
```

## Modeling effect of phase x condition on build time 
```{r}
dpp <- d %>% filter(phase %in% c('pre','post')) 
m3 <- lmer(data = dpp, buildTime ~ phase*condition  + (1 | gameID) + (1 | targetName))
summary(m3)
```

## Import BIS and apply preprocessing
```{r}
b.raw = read.csv('../results/csv/block_silhouette_bis_Exp2Pilot3.csv')

b<-b.raw%>%
  mutate(repetition_1 = repetition + 1)

bpp <- b %>%
  filter(phase %in% c('pre','post'))
bpp
```

## Modeling effect of phase x condition on numBlocks
```{r}
dpp <- d %>% filter(phase %in% c('pre','post')) 
m3 <- lmer(data = dpp, numBlocks ~ phase*condition  + (1 | gameID) + (1 | targetName))
summary(m3)
```

## Model effect of phase * condition on BIS
```{r}
m4 <- lmer(data = bpp, bis ~ phase*condition + (1 | targetName))
summary(m4)
```

## Bootstrap resample condition, repetition
```{r}
bpp.boot <- bpp %>% group_by(condition, phase) %>% tidyboot_mean(column=bis, nboot=100)
bpp.boot
```

```{r}
b.boot <- b %>% group_by(condition, repetition_1) %>% tidyboot_mean(column=bis, nboot=100)
b.boot
```


## Visualize BIS timecourse
```{r}
b.boot %>%
  ggplot(aes(x=repetition_1,y=empirical_stat, color=condition, fill=condition)) +
    geom_ribbon(aes(ymin=ci_lower, ymax = ci_upper), alpha =.25, color=NA,
                data = b.boot %>% filter(condition == 'repeated')) + # position = dodge,
    geom_line(size=1.5)+ 
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,
                  data = b.boot %>% filter(condition == 'control')) +
    geom_point(size = 5) +
    ylab("construction efficiency") +
    xlab("repetition") +
    theme_few() +
    scale_x_continuous(breaks = round(seq(min(b.boot$repetition_1), max(b.boot$repetition_1), by =1),1)) +
    scale_y_continuous(breaks = seq(-0.5,2.5,0.5)) +
    scale_color_manual(values=c("#77798c", "#1c373e")) +
    scale_fill_manual(values=c("#77798c", "#1c373e")) +
    theme(legend.position = c(0.8, 0.2), text = element_text(size=18), element_line(size=1), element_rect(size=2, color="#00000"))
ggsave('../results/plots/block_silhouette_BIS_timeseries.pdf', width=14, height = 10, units='cm', useDingbats = F)
```

## Model relationship between pre-quartiles and pre-plan-reuse
```{r}
q.raw = read.csv('../results/csv/block_silhouette_placement_quartiles_Exp2Pilot3.csv')
q<-q.raw %>% 
  mutate(quartile = factor(f1_quartile, levels = c("lowest","mid-low","mid-high","highest"))) %>%
  mutate(quartile.numeric = as.numeric(quartile)) %>%
  rename("reused" = "prop_unchanged") %>%
  select(c('gameID','quartile','reused','quartile.numeric'))
  
```

## Model relationship between pre quartile and reused proportion
```{r}
m <- lmer(data = q, reused ~ quartile + (1 | gameID))
summary(m)
```

```{r}
m <- lmer(data = q, reused ~ quartile.numeric + (1 | gameID))
summary(m)
```

```{r}
q
```

## Bootstrap resample reused proportion by quartile
```{r}
q.boot <- q %>% group_by(quartile.numeric) %>% tidyboot_mean(column=reused, nboot=100)
q.boot
```

```{r}
q.boot %>%
  ggplot(aes(x=quartile.numeric,y=empirical_stat)) +
  # geom_ribbon(aes(ymin=ci_lower, ymax = ci_upper), alpha =.25, color="#1c373e", fill="#1c373e") +
  geom_smooth(method='lm', formula = y ~ poly(x,1), color="#1c373e", fill="#b1c4c9") +
  geom_point(aes(x=quartile.numeric, y=empirical_stat),color="#1c373e",size = 4) +
  ylab("proportion actions reused (pre to post)") +
  xlab("accuracy quartile (pre)") +
  theme_few() +
  ylim(c(0,0.6)) +
  scale_x_continuous(breaks = c(1,2,3,4),labels=c('low', 'midlow','midhigh','top')) +
  theme(legend.position = c(0.8, 0.2), text = element_text(size=14), element_line(size=1), element_rect(size=2, color="#00000"))  
ggsave('../results/plots/block_silhouette_reuse_quartile.pdf', width=7, height = 10, units='cm', useDingbats = F)

```

## Bootstrap resample reused proportion by quartile
```{r}
dpp <- d %>% filter(phase %in% c('pre','post'))  %>% mutate(phase.numeric = as.numeric(phase))
dpp.boot <- dpp %>% group_by(phase) %>% tidyboot_mean(column=numBlocks, nboot=100)
dpp.boot
```


## Visualize change in numBlocks as function of repetition
```{r}
dpp.boot %>%
  ggplot(aes(x=phase,y=empirical_stat)) +
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,data = dpp.boot) +
    geom_point(aes(x=phase, y=empirical_stat),color="#1c373e",size = 4) +
    # geom_smooth(method='lm', formula = y ~ poly(x,1), color="#1c373e", fill="#b1c4c9") +
    ylab("number of blocks") +
    xlab("phase") +
    theme_few() +
    ylim(c(6,12)) +
    # scale_x_continuous(breaks = round(seq(min(dpp.boot$phase), max(dpp.boot$phase), by =1),1)) +
    # scale_y_continuous(breaks = seq(0,2,10)) +
    scale_color_manual(values=c("#77798c", "#1c373e")) +
    scale_fill_manual(values=c("#77798c", "#1c373e")) +
    theme(legend.position = c(0.75, 0.2), text = element_text(size=14), element_line(size=1), element_rect(size=2, color="#00000"))
ggsave('../results/plots/block_silhouette_numBlocks_timeseries.pdf', width=7, height = 10, units='cm', useDingbats = F)
```

## To what extent do numBlocks and planReuse predict learning?
```{r}
q
```

