---
title: "block silhouette analysis"
author: "wmccarthy & jefan"
date: "12/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)
library(brms)
library(tidyboot)
```

# Import group data

```{r}
d <- read_csv('../results/csv/block_silhouette_pilot3.csv') 
d
```

# Modeling ACCURACY (normedScore) from condition, with random intercepts for participant and target

## Model specifications

```{r}
## fixed effects only
m1 <- lm(normedScore ~ condition, 
            data = d)

## with random intercepts for participant only
m2 <- lmer(normedScore ~ condition + (1 | gameID),
            data = d)

## with random intercepts for item only
m3 <- lmer(normedScore ~ condition + (1 | targetName),
            data = d)

##with random intercepts for both participant AND item
m4 <- lmer(normedScore ~ condition + (1 | gameID) + (1 | targetName),
            data = d)

```

### Model comparison
```{r}
anova(m2,m3,m4)
```

### Model inspection

```{r}
summary(m4)
```

# Define basic model predicting BLOCK EFFICIENCY (numBlocks) from condition, with random intercepts for participant and target


```{r}
## fixed effects only
m1 <- lm(numBlocks ~ condition, 
            data = d)

## with random intercepts for participant only
m2 <- lmer(numBlocks ~ condition + (1 | gameID),
            data = d)

## with random intercepts for item only
m3 <- lmer(numBlocks ~ condition + (1 | targetName),
            data = d)

##with random intercepts for both participant AND item
m4 <- lmer(numBlocks ~ condition + (1 | gameID) + (1 | targetName),
            data = d)

```


### Model comparison
```{r}
anova(m2,m3,m4)
```

### Model inspection
```{r}
summary(m4)
```

# Define basic model predicting BUILD DURATION (TBD) from condition, with random intercepts for participant and target

### Model specification
```{r}
## see above

```


### Model comparison
```{r}
## see above

```

### Model inspection
```{r}
## see above

```