---
title: "block_silhouette_"
author: "wmccarthy & jefan"
date: "5/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(broom)
library(tidyverse)
library(tidyboot)
library(knitr)
library(ggplot2)
library(ggthemes)
library(broom)
library(lme4)
library(lmerTest)
library(numform)
knitr::opts_chunk$set(echo = TRUE)
```

## Import data and apply preprocessing

```{r import}

iterationName = 'Exp2Pilot3_all'

df.full = read.csv(paste('../../results/csv/block_silhouette_',iterationName,'_good.csv', sep=''))

d <- df.full %>%
  select(rawF1DiscreteScore,phase,phase_extended,phase_number,condition,trialNum,targetName,gameID,numBlocks,repetition,blockFell,buildTime,buggy,perfectScore,meanIBI,thinkingTime) %>%
  rename('preparationTime'='thinkingTime') %>%
  rename('accuracy'='rawF1DiscreteScore') %>%
  mutate(phase=factor(phase, levels=c('pre','repeated','post'))) %>%
  mutate(phase_extended=factor(phase_extended, levels=c("pre","repeated","post"))) %>%
  mutate(blockFell = as.logical(blockFell)) %>%
  mutate(perfect = ifelse(accuracy>0.99, TRUE, FALSE)) %>% 
  mutate(buildTimeSec = buildTime/1000)

dpp <- d %>% filter(phase %in% c('pre','post')) %>%
  mutate(phase = factor(phase,levels=c("pre","post")))
```

```{r phase.accuracy}

dpp.boot<-dpp %>%
  group_by(phase_number) %>%
  tidyboot_mean(column=accuracy, nboot=1000)

dpp.boot

```
```{r condition.acc}

dpp.boot<-dpp %>%
  group_by(condition) %>%
  tidyboot_mean(column=accuracy, nboot=1000)

dpp.boot

```

```{r phase.perfect}

# dperf <- d %>%
#   mutate(perfect = ifelse(perfectScore, 1, 0)) 
# 
# dperf.boot<- dperf %>%
#   group_by(phase_number) %>% 
#   tidyboot_mean(column=perfect, nboot=100)
# 
# dperf.boot

```

```{r structure.accuracy}
dstruct.boot <- dpp %>%
  group_by(targetName,phase) %>%
  tidyboot_mean(column=accuracy, nboot=1000)

dstruct.boot
```

```{r}
d.blockFell <- dpp %>% 
  group_by(phase) %>% 
  tidyboot_mean(column=blockFell, nboot=1000)

d.blockFell

```




```{r}
## fit model to data just comparing pre/post
dpp <- d %>% filter(phase %in% c('pre','post')) %>% mutate(phase = factor(phase,levels=c("pre","post")))
m1 <- lmer(data = dpp, accuracy ~ phase + (1 | gameID) + (1 | targetName))
m2 <- lmer(data = dpp, accuracy ~ condition + (1 | gameID) + (1 | targetName))
m3 <- lmer(data = dpp, accuracy ~ phase + condition + (1 | gameID) + (1 | targetName))
m4 <- lmer(data = dpp, accuracy ~ phase * condition + (1 | gameID) + (1 | targetName))
anova(m1,m2,m3,m4)
summary(m4)

```

## Visualize change in accuracy
```{r}

dpp.boot<- d %>%
  group_by(phase_number,condition) %>%
  tidyboot_mean(column=accuracy, nboot=1000)

dpp.boot %>%
  ggplot(aes(x=phase_number,y=empirical_stat, color=condition, fill=condition)) +
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,
                  data = dpp.boot %>% filter(condition == 'control')) +  
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,
                data = dpp.boot %>% filter(condition == 'repeated')) + # position = dodge,
    geom_line(size=1.5)+
    geom_point(size = 4) +
    ylab("F1 score") +
    xlab("attempt") +
    theme_few() +
    # scale_x_continuous(breaks = round(seq(1, 4, by =1),1)) +
    xlim(c(0.5,4.5)) +  
    ylim(c(0.6,1)) +
    scale_x_continuous(limits = c(0.6,4.4), breaks = c(1,2,3,4),labels=c('first', '2nd','3rd','final')) +
    # scale_y_continuous(breaks = seq(-0.5,2.5,0.5)) +
    scale_color_manual(values=c("#77798c", "#1c373e")) +
    scale_fill_manual(values=c("#77798c", "#1c373e")) +
    theme(legend.position = 'FALSE', text = element_text(size=16), element_line(size=1), element_rect(size=2, color="#00000"))
ggsave('../results/plots/cogsci/block_silhouette_accuracy_timeseries.pdf', width=7, height = 10, units='cm', useDingbats = F)
```
## build time
```{r}
dpp.boot <- d %>%
  filter(blockFell==FALSE) %>% 
  group_by(phase_number, condition) %>%
  tidyboot_mean(column=buildTimeSec, nboot=1000)

dpp.boot
```

## Visualize buildTime timecourse
```{r}
dpp.boot %>%
  ggplot(aes(x=phase_number,y=empirical_stat, color=condition, fill=condition)) +
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,
                data = dpp.boot %>% filter(condition == 'repeated')) + # position = dodge,
    geom_line(size=1.5)+ 
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,
                  data = dpp.boot %>% filter(condition == 'control')) +
    geom_point(size = 5) +
    ylab("build time (s)") +
    xlab("attempt") +
    theme_few() +
    scale_x_continuous(breaks = round(seq(1, 4, by =1),1)) +
    xlim(c(0.5,4.5)) +
    ylim(c(40,55)) +
    # scale_y_continuous(breaks = seq(30,55, by=5)) +
    scale_color_manual(values=c("#77798c", "#1c373e")) +
    scale_fill_manual(values=c("#77798c", "#1c373e")) +
    scale_x_continuous(breaks = c(1,2,3,4),labels=c('first', '2nd','3rd','final')) +
    theme(legend.position = 'none', text = element_text(size=18), element_line(size=1), element_rect(size=2, color="#00000"))
ggsave('../results/plots/cogsci/block_silhouette_buildTime_timeseries.pdf', width=7, height = 10, units='cm', useDingbats = F)
```
```{r}
d %>% 
  group_by(perfect) %>% 
  tally()

564/(1956+564)
```
```{r}
d
```

## build time
```{r}
dpp.boot <- d %>%
  filter(blockFell==FALSE) %>% 
  #filter(phase %in% c('pre','post')) %>% 
  group_by(phase_number, perfectScore, condition) %>%
  tidyboot_mean(column=buildTimeSec, nboot=1000)

dpp.boot
```

## Visualize buildTime timecourse with perfect structures
```{r}
dpp.boot %>%
  ggplot(aes(x=phase_number,y=empirical_stat, color=condition)) +
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,
                data = dpp.boot %>% filter(perfectScore == 'True')) + # position = dodge,
    geom_line(size=1.5,data = dpp.boot %>% filter(perfectScore == 'True')) +
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,
                  data = dpp.boot %>% filter(perfectScore == 'False')) +
    geom_line(size=1.5,data = dpp.boot %>% filter(perfectScore == 'False'), linetype='dashed') +
    geom_point(size = 4) +
    ylab("build time (s)") +
    xlab("attempt") +
    theme_few() +
    #scale_x_continuous(breaks = round(seq(1, 4, by =1),1)) +
    xlim(c(0.5,4.5)) +
    #ylim(c(40,55)) +
    #scale_y_continuous(breaks = seq(30,55, by=5)) +
    scale_y_continuous(breaks = 5, limits = c(35,60)) + 
    scale_x_continuous(limits = c(0.6,4.4), breaks = c(1,2,3,4),labels=c('first', '2nd','3rd','final')) +
    scale_color_manual(values=c("#77798c", "#1c373e")) +
    scale_fill_manual(values=c("#77798c", "#1c373e")) +
    theme(legend.position = 'none',text = element_text(size=16), element_line(size=1), element_rect(size=2, color="#00000"))
ggsave('../results/plots/cogsci/block_silhouette_buildTime_timeseries_withperfect.pdf', width=7, height = 10, units='cm', useDingbats = F)
```
### Model for build time
```{r}
## fit model to data just comparing pre/post
dpp <- d %>% 
  filter(phase %in% c('pre','post')) %>% 
  mutate(phase = factor(phase,levels=c("pre","post"))) %>% 
  filter(blockFell==FALSE)

m1 <- lmer(data = dpp, buildTimeSec ~ phase + (1 | gameID) + (1 | targetName))
m2 <- lmer(data = dpp, buildTimeSec ~ condition + (1 | gameID) + (1 | targetName))
m3 <- lmer(data = dpp, buildTimeSec ~ phase + condition + (1 | gameID) + (1 | targetName))
m4 <- lmer(data = dpp, buildTimeSec ~ phase + condition + perfectScore + (1 | gameID) + (1 | targetName))
m5 <- lmer(data = dpp, buildTimeSec ~ phase * condition + perfectScore + (1 | gameID) + (1 | targetName))
m6 <- lmer(data = dpp, buildTimeSec ~ phase * perfectScore * condition +  (1 | gameID) + (1 | targetName))
anova(m1,m2,m3,m4,m5,m6)
summary(m4)
```

```{r}
## fit model to data just comparing pre/post
dpp <- d %>% 
  filter(phase %in% c('pre','post')) %>% 
  mutate(phase = factor(phase,levels=c("pre","post"))) %>% 
  filter(blockFell==FALSE)

m1 <- lmer(data = dpp, buildTimeSec ~ phase + (1 | gameID) + (1 | targetName))
m2 <- lmer(data = dpp, buildTimeSec ~ condition + (1 | gameID) + (1 | targetName))
m3 <- lmer(data = dpp, buildTimeSec ~ phase + condition + (1 | gameID) + (1 | targetName))
m4 <- lmer(data = dpp, buildTimeSec ~ phase + condition + perfectScore + (1 | gameID) + (1 | targetName))
m5 <- lmer(data = dpp, buildTimeSec ~ phase + condition * perfectScore + (1 | gameID) + (1 | targetName))
m6 <- lmer(data = dpp, buildTimeSec ~ phase * perfectScore * condition +  (1 | gameID) + (1 | targetName))
anova(m1,m2,m3,m4,m5,m6)
summary(m5)
```

```{r}
## fit model to data just comparing pre/post
dpp <- d %>% 
  filter(phase %in% c('pre','post')) %>% 
  mutate(phase = factor(phase,levels=c("pre","post"))) %>% 
  filter(blockFell==FALSE)

m1 <- lmer(data = dpp, buildTimeSec ~ phase + (1 | gameID) + (1 | targetName))
m2 <- lmer(data = dpp, buildTimeSec ~ condition + (1 | gameID) + (1 | targetName))
m3 <- lmer(data = dpp, buildTimeSec ~ phase + perfectScore + (1 | gameID) + (1 | targetName))
m4 <- lmer(data = dpp, buildTimeSec ~ phase + perfectScore + condition + (1 | gameID) + (1 | targetName))
m5 <- lmer(data = dpp, buildTimeSec ~ phase * perfectScore + condition + (1 | gameID) + (1 | targetName))
m6 <- lmer(data = dpp, buildTimeSec ~ phase * perfectScore * condition +  (1 | gameID) + (1 | targetName))
anova(m1,m2,m3,m4,m5,m6)
summary(m5)
```

```{r}
d 
```

```{r}
# add column with accuracy of previous attempt

d

accuracies <- d %>%
  mutate(next_phase_number = phase_number+1) %>% 
  mutate(previous_accuracy = accuracy) %>% 
  mutate(previous_buildTimeSec = buildTimeSec) %>% 
  mutate(previous_blockFell = blockFell) %>% 
  select(c(condition,next_phase_number,targetName,previous_accuracy,previous_buildTimeSec,previous_blockFell,gameID))

#update control variables as next phase is post
index <- (accuracies$condition == 'control') & (accuracies$next_phase_number == 2)
accuracies$next_phase_number[index] <- 4

d.withprev <- d %>%
  inner_join(accuracies, by = c('condition'='condition',
                                'targetName'='targetName',
                                'gameID'='gameID',
                                'phase_number'='next_phase_number'))

d.withprev <- d.withprev %>% 
  mutate(previous_perfect = d.withprev$previous_accuracy==1) %>% 
  mutate(diff_time = buildTimeSec-previous_buildTimeSec)


d.withprev %>%
  group_by(phase_number) %>%
  tally()

d.withprev

```

```{r}
# BT ~ attempt + condition + perfect_{t-1} + attempt*perfect_{t-1} + (1 + attempt*perfect_{t-1} | gameID) + (1 + attempt*perfect_{t-1} | targetID)

time.data <- d.withprev %>% 
  filter(condition=='repeated') %>% 
  filter(previous_blockFell==FALSE)

m1 <- lmer(data = time.data, diff_time ~
             phase_number +
             previous_accuracy +
             (1 | gameID) +
             (1 | targetName))

summary(m1)
```

```{r}
d.withprev %>% filter(condition=='repeated') %>% 
  ggplot(aes(x=previous_accuracy, y=diff_time, color = previous_blockFell)) +
  geom_point()
```

```{r}
d.withprev %>% filter(condition=='repeated') %>% 
  ggplot(aes(x=previous_accuracy, y=accuracy, color = previous_blockFell)) +
  geom_point()
```

```{r}
m1 <- lmer(data = d.withprev, buildTimeSec ~ 
             phase_number + 
             condition +
             previous_accuracy + 
             phase_number * previous_accuracy +
             (1 + phase_number | gameID) +
             (1 + phase_number * previous_accuracy | targetName))

summary(m1)

# BT ~ attempt + condition + perfect_{t-1} + attempt*perfect_{t-1} + (1 + attempt*perfect_{t-1} | gameID) + (1 + attempt*perfect_{t-1} | targetID)


```


# Number of blocks
```{r}
dpp.nblocks.boot <- d %>% group_by(phase_number,condition) %>% tidyboot_mean(column=numBlocks, nboot=1000)
dpp.nblocks.boot %>%
  ggplot(aes(x=phase_number,y=empirical_stat,fill=condition)) +
    geom_bar(stat="identity", aes(x=phase_number, y=empirical_stat,fill=condition), position=position_dodge(.9)) +
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,position=position_dodge(.9)) +
    # geom_point(aes(x=phase, y=empirical_stat),color="#1c373e", size=4) +
    # geom_smooth(method='lm', formula = y ~ poly(x,1), color="#1c373e", fill="#b1c4c9") +
    ylab("number of blocks") +
    xlab("phase") +
    theme_few() +
    ylim(c(0,14)) +
    # scale_x_continuous(breaks = round(seq(min(dpp.boot$phase), max(dpp.boot$phase), by =1),1)) +
    # scale_y_continuous(breaks = seq(0,2,10)) +
    scale_color_manual(values=c("#77798c", "#1c373e")) +
    scale_fill_manual(values=c("#77798c", "#1c373e")) +
    theme(legend.position = c(0.35, 0.85), text = element_text(size=14), element_line(size=1), element_rect(size=2, color="#00000"))
#ggsave('../results/plots/block_silhouette_numBlocks_timeseries.pdf', width=7, height = 10, units='cm', useDingbats = F)
```

```{r}
## fit model to data just comparing pre/post
dpp <- d %>% filter(phase %in% c('pre','post')) %>% mutate(phase = factor(phase,levels=c("pre","post"))) %>% 
  filter(blockFell==FALSE)
m1 <- lmer(data = dpp, numBlocks ~ phase + (1 | gameID) + (1 | targetName))
m2 <- lmer(data = dpp, numBlocks ~ condition + (1 | gameID) + (1 | targetName))
m3 <- lmer(data = dpp, numBlocks ~ phase + condition + (1 | gameID) + (1 | targetName))
m4 <- lmer(data = dpp, numBlocks ~ phase * condition + (1 | gameID) + (1 | targetName))
anova(m1,m2,m3,m4)
summary(m3)
```

# Task fluency (inter-block-interval)
```{r}
dpp <- d %>% filter(phase %in% c('pre','post')) %>% mutate(phase = factor(phase,levels=c("pre","post")))
m1 <- lmer(data = dpp, meanIBI ~ phase + (1 | gameID) + (1 | targetName))
m2 <- lmer(data = dpp, meanIBI ~ condition + (1 | gameID) + (1 | targetName))
m3 <- lmer(data = dpp, meanIBI ~ phase + condition + (1 | gameID) + (1 | targetName))
m4 <- lmer(data = dpp, meanIBI ~ phase * condition + (1 | gameID) + (1 | targetName))
anova(m1,m2,m3,m4)
summary(m4)
```


# Preparation time (time before first block placement)
```{r}
dpp <- d %>% filter(phase %in% c('pre','post')) %>% mutate(phase = factor(phase,levels=c("pre","post")))
m1 <- lmer(data = dpp, preparationTime ~ phase + (1 | gameID) + (1 | targetName))
m2 <- lmer(data = dpp, preparationTime ~ condition + (1 | gameID) + (1 | targetName))
m3 <- lmer(data = dpp, preparationTime ~ phase + condition + (1 | gameID) + (1 | targetName))
m4 <- lmer(data = dpp, preparationTime ~ phase * condition + (1 | gameID) + (1 | targetName))
anova(m1,m2,m3,m4)
summary(m4)
```

# Actions

```{r import.actions}
df.action.metrics.full = read.csv('../results/csv/block_silhouette_Exp2Pilot3_all_rep_distances.csv')

df.action.metrics.full
```

```{r}
df.Euclidean.long <- df.action.metrics.full %>% 
  # mutate(phase.pair.numeric = as.numeric(phase_pair)) %>% 
  select(gameID,targetName, phase_a_rawF1DiscreteScore, phase_pair,actual_euclidean_distance,optimal_euclidean_distance) %>%
  pivot_longer(c(optimal_euclidean_distance,actual_euclidean_distance), names_to='distance_type') %>% 
  rename("euclidean_distance" = "value")


df.Euclidean.long$distance_type = gsub("\\_.*","",df.Euclidean.long$distance_type)
df.Euclidean.long
```


```{r}

d.Eu <- df.Euclidean.long %>% 
  filter(phase_pair %in% c('pre to repetition 1', 'repetition 1 to repetition 2','repetition 2 to post')) %>% 
  mutate(phase_pair = ordered(phase_pair,levels=c('pre to repetition 1','repetition 1 to repetition 2','repetition 2 to post'))) %>% within(df.Euclidean.long, phase_pair <- relevel(phase_pair, ref = 'pre to repetition 1'))

d.Eu.boot<-d.Eu %>%
  group_by(phase_pair,distance_type) %>%
  tidyboot_mean(column=euclidean_distance, nboot=1000)

d.Eu.boot

```

```{r}
d.Eu.boot %>%
  ggplot(aes(x=phase_pair,y=empirical_stat, color=distance_type, fill=distance_type, group = distance_type)) +
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,
                 data = d.Eu.boot %>% filter(distance_type == 'actual')) +  
    geom_errorbar(aes(ymin=ci_lower, ymax = ci_upper), width = 0, size = 1.5,
                 data = d.Eu.boot %>% filter(distance_type == 'optimal')) +
    geom_line(size=1.5) +
    geom_point(size = 4) +
    ylab("Euclidean distance") +
    xlab("attempt pair") +
    theme_few() +
    #xlim(c(0.5,3.5)) +  
    ylim(c(0,4.5)) +
    # scale_y_continuous(breaks = seq(-0.5,2.5,0.5)) +
    scale_color_manual(values=c("#77798c","#1c373e")) +
    scale_fill_manual(values=c("#77798c","#1c373e")) +
    scale_x_discrete(labels= c(1,2,3)) + 
    theme(legend.position ='FALSE', legend.title=element_blank(), text = element_text(size=16), element_line(size=1), element_rect(size=2, color="#00000"))
ggsave('../results/plots/block_silhouette_Euclidean_distances.pdf', width=7, height = 10, units='cm', useDingbats = F)
```


```{r}
m1 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair + (1 | gameID) + (1 | targetName))
m2 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair + distance_type + (1 | gameID) + (1 | targetName))
m3 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair * distance_type + (1 | gameID) + (1 | targetName))
m4 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair * distance_type + (1 | gameID) + (1 | targetName))
anova(m1,m2,m3,m4)
summary(m4)
```
# Full models of Euclidean distance

```{r}
d.Eu <- d.Eu %>% 
  mutate(phase_pair = as.numeric(phase_pair))
```


```{r}
m1 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair + (1 | gameID) + (1 | targetName))
m2 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair + distance_type + (1 | gameID) + (1 | targetName))
m3 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair + distance_type + phase_a_rawF1DiscreteScore + (1 | gameID) + (1 | targetName))
m4 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair * distance_type + phase_a_rawF1DiscreteScore + (1 | gameID) + (1 | targetName))
m5 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair * distance_type * phase_a_rawF1DiscreteScore + (1 | gameID) + (1 | targetName))
anova(m1,m2,m3,m4,m5)
summary(m4)
```

```{r}
m1 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair + (1 | gameID) + (1 | targetName))
m2 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair + distance_type + (1 | gameID) + (1 | targetName))
m3 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair + distance_type + phase_a_rawF1DiscreteScore + (1 | gameID) + (1 | targetName))
m4 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair + distance_type * phase_a_rawF1DiscreteScore + (1 | gameID) + (1 | targetName))
m5 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair * distance_type * phase_a_rawF1DiscreteScore + (1 | gameID) + (1 | targetName))
anova(m1,m2,m3,m4,m5)
summary(m4)
```

```{r}
m1 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair + (1 | gameID) + (1 | targetName))
m2 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair + distance_type + (1 | gameID) + (1 | targetName))
m3 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair + distance_type + phase_a_rawF1DiscreteScore + (1 | gameID) + (1 | targetName))
m4 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair * phase_a_rawF1DiscreteScore + distance_type + (1 | gameID) + (1 | targetName))
m5 <- lmer(data = d.Eu, euclidean_distance ~ phase_pair * distance_type * phase_a_rawF1DiscreteScore + (1 | gameID) + (1 | targetName))
anova(m1,m2,m3,m4,m5)
summary(m4)
```


## Derivative plots (consequetive phases)

```{r derivative}
d.derivative <- df.action.metrics.full %>% 
  filter(phase_pair %in% c('pre to repetition 1', 'repetition 1 to repetition 2','repetition 2 to post'))
```

```{r}
## fit model for mean Euclidean distance of best action mapping
m1 <- lmer(data = d.derivative, actual_euclidean_distance ~ phase_pair + (1 | gameID) + (1 | targetName))
m2 <- lmer(data = d.derivative, actual_euclidean_distance ~ phase_pair + phase_a_rawF1DiscreteScore + (1 | gameID) + (1 | targetName))
m3 <- lmer(data = d.derivative, actual_euclidean_distance ~ phase_pair * phase_a_rawF1DiscreteScore + (1 | gameID) + (1 | targetName))
anova(m1,m2,m3)
summary(m2)
```



```{r}
## fit model for mean Euclidean distance of best action mapping
m1 <- lmer(data = d.derivative, optimal_euclidean_distance ~ phase_pair + (1 | gameID) + (1 | targetName))
m2 <- lmer(data = d.derivative, optimal_euclidean_distance ~ phase_pair + phase_a_rawF1DiscreteScore + (1 | gameID) + (1 | targetName))
m3 <- lmer(data = d.derivative, optimal_euclidean_distance ~ phase_pair * phase_a_rawF1DiscreteScore + (1 | gameID) + (1 | targetName))
anova(m1,m2,m3)
summary(m2)
```


# Sequence Similarity predicted by F1 score
Does high performance mean that similar build sequences will be used next time?

##Looking only at pre and post:



### Find quartiles of pretest accuracy (QUARTILES OF THAT SUBSET- SHOULD THIS BE QUARTILES OF WHOLE DATASET?)
```{r}
dpp <- df.action.metrics.full %>% 
  filter(phase_a=='pre' & phase_b=='post')

# quartiles for everyone
# dpp$pre.f1.quartile <- ntile(dpp$phase_a_rawF1DiscreteScore, 4) 

# quartile for that subject
dpp <- dpp %>%
  group_by(gameID) %>% 
  mutate(pre.f1.quartile=ntile(phase_a_rawF1DiscreteScore, 4))
```

```{r}
dpp
```

See if people make more radical updates to plans when they've acquired more task-general knowledge
```{r}
d.attempt <- df.action.metrics.full %>% 
  filter((condition=='control' & phase_pair=='pre to post') | (condition=='repeated' & phase_pair=='pre to repetition 1'))

m1 <- lmer(data = d.attempt, optimal_euclidean_distance ~ condition + (1 | gameID) + (1 | targetName))
summary(m1)
```

```{r attempt.similarity}
d.attempt <- df.action.metrics.full %>% 
  filter(phase_pair %in% c('pre to repetition 1', 'repetition 1 to repetition 2','repetition 2 to post'))
```


## Optimal Euclidean Distance

### Model relationship between pre quartile and optimal Euclidean similarity
```{r}
m <- lmer(data = dpp, optimal_euclidean_distance ~ pre.f1.quartile + (1 | gameID) +  (1 | targetName))
summary(m)
```

```{r}
dpp.Eu <- dpp %>% select(c('gameID','pre.f1.quartile','actual_euclidean_distance'))
dpp.boot.Eu <- dpp %>% group_by(pre.f1.quartile) %>% tidyboot_mean(column=actual_euclidean_distance, nboot=1000)
dpp.boot.Eu
```

```{r}
dpp.boot.Eu %>%
  ggplot(aes(x=pre.f1.quartile,y=empirical_stat)) +
  # geom_ribbon(aes(ymin=ci_lower, ymax = ci_upper), alpha =.25, color="#1c373e", fill="#1c373e") +
  geom_point(aes(x=pre.f1.quartile, y=actual_euclidean_distance), data=dpp.Eu, size = 3, alpha = 0.5, color="#b1c4c9") +
  geom_smooth(method='lm', formula = y ~ poly(x,1), color="#1c373e", fill="#b1c4c9") +
  geom_point(aes(x=pre.f1.quartile, y=empirical_stat),color="#1c373e",size = 5) +
  ylab("Mean euclidean distance between pre to post actions") +
  xlab("accuracy quartile (pre)") +
  theme_few() +
  #ylim(c(0,0.6)) +
  scale_x_continuous(breaks = c(1,2,3,4),labels=c('1st', '2nd','3rd','4th')) +
  theme(legend.position = c(0.8, 0.2), text = element_text(size=14), element_line(size=1), element_rect(size=2, color="#00000"))
```

```{r}
m <- lmer(data = dpp, optimal_euclidean_distance ~ pre.f1.quartile + (1 | gameID) + (1 | targetName))
summary(m)
```

```{r}
dpp.OEu <- dpp %>% select(c('gameID','pre.f1.quartile','optimal_euclidean_distance'))
dpp.boot.OEu <- dpp %>% group_by(pre.f1.quartile) %>% tidyboot_mean(column=optimal_euclidean_distance, nboot=1000)
dpp.boot.OEu
```

```{r}
dpp.boot.OEu %>%
  ggplot(aes(x=pre.f1.quartile,y=empirical_stat)) +
  # geom_ribbon(aes(ymin=ci_lower, ymax = ci_upper), alpha =.25, color="#1c373e", fill="#1c373e") +
  geom_point(aes(x=pre.f1.quartile, y=optimal_euclidean_distance), data=dpp.OEu, size = 3, alpha = 0.5, color="#b1c4c9") +
  geom_smooth(method='lm', formula = y ~ poly(x,1), color="#1c373e", fill="#b1c4c9") +
  geom_point(aes(x=pre.f1.quartile, y=empirical_stat),color="#1c373e",size = 5) +
  ylab("Euclidean distance") +
  xlab("accuracy quartile (pre)") +
  theme_few() +
  ylim(c(0,5)) +
  scale_x_continuous(breaks = c(1,2,3,4),labels=c('1st', '2nd','3rd','4th')) +
  theme(legend.position = c(0.8, 0.2), text = element_text(size=16), element_line(size=1), element_rect(size=2, color="#00000"))

ggsave('../results/plots/block_silhouette_accuracy_seq_diff.pdf', width=7, height = 10, units='cm', useDingbats = F)
```


```{r}

d.conseq <- df.action.metrics.full %>% 
  filter(phase_pair %in% c('pre to repetition 1','repetition 1 to repetition 2', 'repetition 2 to post'))

# quartiles for everyone
#d.conseq$phase_a.f1.quartile <- ntile(d.conseq$phase_a_rawF1DiscreteScore, 4)

# quartile for that subject
d.conseq <- d.conseq %>%
  group_by(gameID) %>% 
  mutate(phase_a.f1.quartile=ntile(phase_a_rawF1DiscreteScore, 4))


#d.conseq.OEu <- d.conseq %>% select(c('gameID','phase_a.f1.quartile','optimal_euclidean_distance'))
d.conseq.boot.OEu <- d.conseq %>% group_by(phase_pair,phase_a.f1.quartile) %>% tidyboot_mean(column=optimal_euclidean_distance, nboot=1000)
d.conseq.boot.OEu
```

```{r}
d.conseq.boot.OEu %>%
  ggplot(aes(x=phase_a.f1.quartile,y=empirical_stat)) +
  # geom_ribbon(aes(ymin=ci_lower, ymax = ci_upper), alpha =.25, color="#1c373e", fill="#1c373e") +
  geom_point(aes(x=phase_a.f1.quartile, y=optimal_euclidean_distance), data=d.conseq, size = 3, alpha = 0.5, color="#b1c4c9") +
  geom_smooth(method='lm', formula = y ~ poly(x,1), color="#1c373e", fill="#b1c4c9") +
  geom_point(aes(x=phase_a.f1.quartile, y=empirical_stat, color = phase_pair),size = 5) +
  ylab("Euclidean distance") +
  xlab("first phase accuracy quartile") +
  theme_few() +
  #ylim(c(0,4)) +
  scale_x_continuous(breaks = c(1,2,3,4),labels=c('1st', '2nd','3rd','4th')) +
  theme(legend.position = c(0.8, 0.8), text = element_text(size=16), element_line(size=1), element_rect(size=2, color="#00000"))
```

```{r}
d.conseq %>% 
  ggplot(aes(x=phase_a_rawF1DiscreteScore, y = optimal_euclidean_distance,color=phase_pair)) +
  geom_point(size = 0.2) +
  ylab("Euclidean distance") +
  xlab("F1 in previous attempt") +
  geom_smooth(method='lm', formula = y ~ poly(x,1)) +
  ylim(c(0,4.5)) +
  theme_few() +
  scale_color_manual(values=c("#EF553B","#B8422E","#70281C")) +
  theme(legend.position = 'FALSE',text = element_text(size=16), element_line(size=1), element_rect(size=2, color="#00000"))
ggsave('../results/plots/block_silhouette_accuracy_seq_diff.pdf', width=7, height = 10, units='cm', useDingbats = F)

```

```{r}
## fit model for mean Euclidean distance of best action mapping
m1 <- lmer(data = d.conseq, optimal_euclidean_distance ~ phase_pair + (1 | gameID) + (1 | targetName))
m2 <- lmer(data = d.conseq, optimal_euclidean_distance ~ phase_pair + phase_a_rawF1DiscreteScore + (1 | gameID) + (1 | targetName))
m3 <- lmer(data = d.conseq, optimal_euclidean_distance ~ phase_pair * phase_a_rawF1DiscreteScore + (1 | gameID) + (1 | targetName))
anova(m1,m2,m3)
summary(m2)
```




# Between-subject variance in action sequences
```{r import.btw.ppt}
# here variance is calculated with both conditions lumped together
ppt.var <- read.csv('../results/csv/block_silhouette_Exp2Pilot3_all_ppt_variance.csv')
ppt.var

# here variance is calculated separately for conditions
#ppt.var.sep <- read.csv('../results/csv/block_silhouette_Exp2Pilot3_all_ppt_variance_separate.csv')
#ppt.var.sep
```

```{r}
ppt.var %>% 
  filter(phase_extended %in% c('pre','post')) %>% 
  mutate(phase_extended = ordered(phase_extended,levels=c('pre','post'))) %>%
  ggplot(aes(x=phase_extended, y=variance, fill=targetName, group = targetName)) +
  geom_line(size=1.5, color="#1c373e") +
  geom_point(size = 4, color="#1c373e") +
  ylab("action variability") +
  xlab("attempt") +
  ylim(c(0,4)) + 
  theme_few() +
  #scale_color_manual(values=c("#1c373e","#77798c")) +
  #scale_fill_manual( values=c("#1c373e","#77798c")) +
  scale_x_discrete(labels = c("first","final")) + 
  theme(legend.position = 'FALSE', text = element_text(size=16), element_line(size=1), element_rect(size=2, color="#00000")) +
  guides(size = FALSE, fill=FALSE)
ggsave('../results/plots/block_silhouette_ppt_variance.pdf', width=7, height = 10, units='cm', useDingbats = F)
```


```{r}
ppt.var.mean <- ppt.var %>% 
  filter(phase_extended %in% c('pre','post')) %>% 
  mutate(phase_extended = ordered(phase_extended,levels=c('pre','post')))

ppt.var.mean.pre <- ppt.var.mean %>% 
  filter(phase_extended=='pre')

ppt.var.mean.post <- ppt.var.mean %>% 
  filter(phase_extended=='post')

t.test(ppt.var.mean.pre$variance, ppt.var.mean.post$variance, paired = TRUE, alternative = "greater")
```

```{r}

iterationName = 'Exp2Pilot3_all'
file_path = paste('../results/csv/block_silhouette_',iterationName,'_ngram_gini_final.csv', sep='')

ginis <- read_csv(file_path)

ginis
```


Model distinguishing pre from post
```{r}
human_ginis <- ginis %>% 
  filter(human==TRUE) %>%
  mutate(phase = factor(phase,levels=c("pre","post","random agent")))
```

```{r}
mp.1 <- lm(gini~ nlevel*phase + poly(nlevel,1), 
                data = human_ginis)
mp.2 <- lm(gini~ nlevel*phase + poly(nlevel,2), 
                data = human_ginis)
mp.3 <- lm(gini~ nlevel*phase + poly(nlevel,3), 
                data = human_ginis)
anova(mp.1,mp.2,mp.3)
summary(mp.2)
```
```{r}
mean_human_ginis <- ginis %>% 
  filter(human == 'TRUE') %>% 
  group_by(nlevel,phase) %>% 
  summarise_at(vars(gini),
               list(mean.gini = mean))

mean_human_ginis
```
```{r}
mean_agent_ginis <- ginis %>% 
  filter(human == 'FALSE') %>% 
  group_by(batch, nlevel) %>% 
  summarise_at(vars(gini),
               list(mean.gini = mean)) %>% 
  ungroup()

mean_agent_ginis

grand_mean_agent_ginis <- mean_agent_ginis %>% 
  group_by(nlevel) %>% 
  summarise_at(vars(mean.gini),
               list(grandmean.gini = mean,
                    sd = sd)) %>% 
  ungroup()

grand_mean_agent_ginis
```
```{r}

agent_gini_CIs <- mean_agent_ginis %>% 
  group_by(nlevel) %>% 
   do(tidy(t(quantile(.$mean.gini,probs = c(0.025,0.975)))))

grand_mean_agent_ginis <- left_join(grand_mean_agent_ginis,agent_gini_CIs, cols = c('nlevel'))

grand_mean_agent_ginis

```

```{r}
mean_agent_ginis %>%
  ggplot(aes(x=nlevel)) +
    geom_line(aes(color=phase, y= mean.gini), width = 0, size = 1.5,
                 data = mean_human_ginis) +
    scale_color_manual(values=c("#70281C","#EF553B")) +
    # geom_point(aes(color=phase), width = 0, size = 4
                 # data = mean_human_ginis) +
    geom_line(aes(y=grandmean.gini), width = 0, size =1, 
              data = grand_mean_agent_ginis, color="#77798c", linetype = "dashed") +
    geom_errorbar(aes(ymin=X2.5., ymax = X97.5.), width = 0, size = 1, data = grand_mean_agent_ginis, color="#77798c") +  
    ylab("systematicity (G)") +
    xlab("n") +
    theme_few() +
    #xlim(c(0.5,3.5)) +  
    ylim(c(0,0.65)) +
    scale_y_continuous(labels = numform::ff_num(zero = 0), breaks = 5, limits = c(0,0.65)) + 
    # scale_y_continuous(breaks = seq(-0.5,2.5,0.5)) +
    #scale_fill_manual(values=c("#77798c","#1c373e")) +
    scale_x_continuous(name="sequence length (n)", breaks = 6) + 
    theme(legend.position ='FALSE', legend.title=element_blank(), text = element_text(size=16), element_line(size=1), element_rect(size=2, color="#00000"))
ggsave('../results/plots/giningrams.pdf', width=7, height = 10, units='cm', useDingbats = F)
```